LAGOS lake depth

### 2021-11-10 README.Rmd
title sync
sync title with ms word
updates

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Docker Build](https://img.shields.io/badge/Docker%20Image-jsta/bathymetry-green.svg)](https://cloud.docker.com/repository/docker/jsta/bathymetry)

@@

**Stachelek et al. In prep**. Imperfect slope measurements drive overestimation in standard cone model of lake depth

@@

options(knitr.kable.NA = '-')
knitr::kable(dt)
```

>>>>

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Data DOI](https://img.shields.io/badge/Data-DOI-blue.svg)](https://doi.org/) [![Docker Build](https://img.shields.io/badge/Docker%20Image-jsta/bathymetry-green.svg)](https://cloud.docker.com/repository/docker/jsta/bathymetry)

@@

**Stachelek J.**, P. J. Hanly, P. A., Soranno, Accepted, Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth. Inland Waters.

@@

options(knitr.kable.NA = "-")
knitr::kable(dt)
```
